Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Fix result figure placement
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@53 db7c848b-7755-4df2-b763-8796797afa52
Minor edits.
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@54 db7c848b-7755-4df2-b763-8796797afa52

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Equalizer 2\\Convergence of a Parallel Rendering Framework}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

{\em Equalizers} are an addition to compound trees. They modify parameters of
their respective subtree at runtime to dynamically optimize the resource usage,
by each tuning one aspect of the decomposition. Due to their nature, they are
transparent to application developers, but might have application-accessible
parameters to tune their behavior. Resource equalization is the critical
component for scalable parallel rendering, and therefore the eponym for the
\textsf{Equalizer} project name. \FIXME{ok, this is a bit tricky to have Equalizer as a
name for the framework as well as for this component, can't we change this?
eile: We can't change the product name, and changing the component name will be
hard. In fact, this is an artefact of the sw architecture: The runtime balancing
of resources is the core contribution of Equalizer, and therefore the equalizers
performing this task are the name-givers for the product. Modified paragraph
above for clarity.}

@@

@@

\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/daviddist}
  \caption{\label{fDavidDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the David 2mm data set in
    \fig{fDavid2mm}}
\end{figure*}
\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the spike data set in
    \fig{fVolumes}, left}
\end{figure*}
\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/beechnutdist}
  \caption{\label{fBeechnutDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the beechnut data set in
    \fig{fVolumes}, right}
\end{figure*}
\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/ifdist}
  \caption{\label{fIFDist}Object synchronization using different network
    transports}
\end{figure*}
\clearpage

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

{\em Equalizers} are an addition to compound trees. They modify parameters of
their respective subtree at runtime to dynamically optimize the resource usage,
by each tuning one aspect of the decomposition. Due to their nature, they are
transparent to application developers, but might have application-accessible
parameters to tune their behavior. Resource equalization is the critical
component for scalable parallel rendering, and therefore the eponym for the
\textsf{Equalizer} project name. \FIXME{modified paragraph is ok; but we
still must make sure that the font differs between the Equalizer project and the
Equalizer components consistently throughout the text}

@@

% Was meinst du damit konkret? Die Implementierung verwendet einen impliziten Octtree (dh kein “baum” ist im Speicher, die Koordinaten werden anhand der Tiefe & position implizit berechnet), asynchrones laden von der DataSource, asychronen Upload auf die GPU. Die “source” Datenstruktur kennt Livre nicht, das hängt von der Implementierung der Datasource ab (zZ UVF, RAW (one octree node), Fivox (3D events-to-volume), Cubist (mesh-to-volume)).

% A VisibleNodesVisitor traverses the Octtree to select the nodes based on the given screen space error (~max pixel/voxel) and their availability. How the nodes are selected, in particular when between different neighbour LOD levels is beyond my knowledge. Another (?) visitor is used to select desired nodes, which are submitted to the data loader threads, which use the data source to load them, then upload them (async) and add them to the available set.

@@

\begin{figure*}[p!]\center
  \includegraphics[height=.19\textheight]{images/daviddist}
  \caption{\label{fDavidDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the David 2mm data set in
    \fig{fDavid2mm}}
\end{figure*}
\begin{figure*}[p!]\center
  \includegraphics[height=.19\textheight]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the spike data set in
    \fig{fVolumes}, left}
\end{figure*}
\begin{figure*}[p!]\center
  \includegraphics[height=.19\textheight]{images/beechnutdist}
  \caption{\label{fBeechnutDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the beechnut data set in
    \fig{fVolumes}, right}
\end{figure*}
\begin{figure*}[p!]\center
  \includegraphics[height=.19\textheight]{images/ifdist}
  \caption{\label{fIFDist}Object synchronization using different network
    transports}
\end{figure*}
